Diagnosising the sensitivity of grounding line flux to changes in sub-ice shelf melting

### 2019-07-03 draft_v2/draft_v2.tex
re-organize the folder structure

%\documentclass[10pt,a4paper]{article}
%\usepackage[latin1]{inputenc}
%\usepackage{amsmath}
%\usepackage{amsfonts}
%\usepackage{amssymb}
%\usepackage{graphicx}

% igs2ejournalguide.tex
% v4.00 3-sept-2015

\NeedsTeXFormat{LaTeX2e}

% check that the math fits the two-column format:
% \documentclass[twocolumn]{igs}

% but use this version when submitting your article:
\documentclass[review,oneside]{igs}

% other options are available
%   authors printing on US letter size are advised 
%   to use the slightly shorter [letterpaper] option
% SINGLE COLUMN
%   \documentclass{igs}              
% SINGLE COLUMN, FEWER LINES/PAGE
%   \documentclass[letterpaper]{igs} 
% DOUBLE COLUMN, FEWER LINES/PAGE
%   \documentclass[twocolumn,letterpaper]{igs}

\usepackage{igsnatbib}
\usepackage{appendix}

% check if we are compiling under latex or pdflatex
\ifx\pdftexversion\undefined
\usepackage[dvips]{graphicx}
\else
\usepackage[pdftex]{graphicx}
\usepackage{epstopdf}
\epstopdfsetup{suffix=}
\fi

@@

\author[Zhang and others]{Tong ZHANG,$^1$ Stephen PRICE,$^1$ Matthew HOFFMAN,$^1$ Mauro PEREGO,$^2$ Xylar ASAY-DAVIS$^1$}
\affiliation{%
  $^1$Fluid Dynamics and Solid Mechanics Group, Los Alamos National Laboratory, New Mexico, United States, 87545, USA\\
  $^2$Center for Computing Research, Sandia National Laboratories, P.O. Box 5800, MS 1320, Albuquerque, NM 87185, USA.\\
  Correspondence: Tong Zhang 
  $<$tzhang@lanl.gov$>$}

\abstract{Motivated by previous work using ice flow models to quantify the impacts of ice shelf buttressing on grounding line flux \citep[e.g.,][]{furst2016,reese2018}, we look for an improved physical understanding for how ice dynamics link ice thickness perturbations, via changes in sub-ice shelf melting, to changes in ice shelf buttressing and grounding line flux. More specifically, we seek to define one or more ``metrics'' that are 1) readily calculated from standard ice sheet model outputs and 2) informative with respect to diagnosing the sensitivity of grounding line flux to changes in ice thickness at specific locations on an ice shelf. By studying the ice dynamics for both idealized (MISMIP+) and realistic (Larsen C) ice shelves, we find a strongly direction-dependent buttressing number that links local changes in ice shelf thickness and dynamics with changes in the integrated grounding line flux. This buttressing metric, defined using the first principal stress, is better overall for quantifying changes in grounding line flux than a similar metric defined using the second principal stress or stress along the flow direction. This correlation is possibly controlled by the relative relationship of geometric/dynamic features between the perturbation point and the grounding line, indicating a dynamic (time evolving) sensitivity field of grounding line flux change to basal melt. Unfortunately, this metric only shows a robust relationship with the integrated grounding line flux for regions near the center of an ice shelf; for points too near the grounding line or the calving front, no clear relationship exists between any of the readily calculable metrics explored here and changes in grounding line flux. This motivates our exploration of an adjoint-based method for defining grounding line flux sensitivity to local changes in ice shelf geometry. When using the same idealized case, we demonstrate that this adjoint-based method is equivalent to the sensitivity analysis of \citep{reese2018} while requiring only a single model adjoint solve. We conclude that adjoint-based methods provide a powerful and efficient tool for determining the grounding line flux sensitivity to changes in sub-ice shelf melting.}

\maketitle

\section{Introduction}

@@

\section{Conclusions}

@@

\bibliographystyle{igs}
\bibliography{refs}

%\appendix

\begin{appendices}
\section{Appendix materials}
%\renewcommand\thefigure{\thesection.\arabic{figure}}  
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{figure}{0}

@@

\end{appendices}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{figs/stressDiff.pdf}
%	\caption{An example of stress component changes (\%) across the MISMIP+ ice shelf and grounding line after apply the perturbations at different locations (blue circles). (a) Changes of $\sigma_{p1}$; (b) Changes of $\sigma_{p2}$; (c) Changes of $\sigma_{f}$; (d) Changes of $\sigma_{s}$;.}
%	\label{stressDiff}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{figs/diffStress_diffVel.pdf}
%	\caption{The change percentage of ice speed (blue dots) and stress components (red dots; a--d represents $\sigma_{p1}$, $\sigma_{p2}$, $\sigma_{f}$ and $\sigma_{s}$, respectively) for all cells at the grounding line corresponding to Fig.~\ref{stressDiff}.}
%	\label{stressDiff_velDiff}
%\end{figure}

>>>>

\documentclass[tc, manuscript]{copernicus}

\usepackage{appendix}

% check if we are compiling under latex or pdflatex
%\ifx\pdftexversion\undefined
%\usepackage[dvips]{graphicx}
%\else
%\usepackage[pdftex]{graphicx}
%\usepackage{epstopdf}
%\epstopdfsetup{suffix=}
%\fi

@@

\Author[1]{Tong}{Zhang}
\Author[1]{Stephen}{Price}
\Author[1]{Matthew}{Hoffman}
\Author[2]{Mauro}{Perego}
\Author[1]{Xylar}{Asay-Davis}

\affil[1]{Fluid Dynamics and Solid Mechanics Group, Los Alamos National Laboratory, Los Alamos, NM, 87545, USA}
\affil[2]{Center for Computing Research, Sandia National Laboratories, Albuquerque, NM, 87185, USA}

\runningtitle{Diagnosising the sensitivity of grounding line flux to sub-ice shelf melting}
\runningauthor{T.~Zhang et al.}
\correspondence{T.~Zhang (tzhang@lanl.gov)}

\received{}
\pubdiscuss{} %% only important for two-stage journals
\revised{}
\accepted{}
\published{}

\firstpage{1}
\maketitle

\begin{abstract}
Motivated by previous work using ice flow models to quantify the impacts of ice shelf buttressing on grounding line flux \citep[e.g.,][]{furst2016,reese2018}, we look for an improved physical understanding for how ice dynamics link ice thickness perturbations, via changes in sub-ice shelf melting, to changes in ice shelf buttressing and grounding line flux. More specifically, we seek to define one or more ``metrics'' that are 1) readily calculated from standard ice sheet model outputs and 2) informative with respect to diagnosing the sensitivity of grounding line flux to changes in ice thickness at specific locations on an ice shelf. By studying the ice dynamics for both idealized (MISMIP+) and realistic (Larsen C) ice shelves, we find a strongly direction-dependent buttressing number that links local changes in ice shelf thickness and dynamics with changes in the integrated grounding line flux. This buttressing metric, defined using the first principal stress, is better overall for quantifying changes in grounding line flux than a similar metric defined using the second principal stress or stress along the flow direction. This correlation is possibly controlled by the relative relationship of geometric/dynamic features between the perturbation point and the grounding line, indicating a dynamic (time evolving) sensitivity field of grounding line flux change to basal melt. Unfortunately, this metric only shows a robust relationship with the integrated grounding line flux for regions near the center of an ice shelf; for points too near the grounding line or the calving front, no clear relationship exists between any of the readily calculable metrics explored here and changes in grounding line flux. This motivates our exploration of an adjoint-based method for defining grounding line flux sensitivity to local changes in ice shelf geometry. When using the same idealized case, we demonstrate that this adjoint-based method is equivalent to the sensitivity analysis of \citep{reese2018} while requiring only a single model adjoint solve. We conclude that adjoint-based methods provide a powerful and efficient tool for determining the grounding line flux sensitivity to changes in sub-ice shelf melting.
\end{abstract}

\copyrightstatement{TEXT}

\introduction

@@

\conclusions

@@

\bibliographystyle{copernicus}
\bibliography{refs}

\appendix

\section{Appendix materials}
%\renewcommand\thefigure{\thesection.\arabic{figure}}  
\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{figure}{0}

@@

\noappendix

%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{figs/stressDiff.pdf}
%	\caption{An example of stress component changes (\%) across the MISMIP+ ice shelf and grounding line after apply the perturbations at different locations (blue circles). (a) Changes of $\sigma_{p1}$; (b) Changes of $\sigma_{p2}$; (c) Changes of $\sigma_{f}$; (d) Changes of $\sigma_{s}$;.}
%	\label{stressDiff}
%\end{figure}
%
%\begin{figure}
%	\centering
%	\includegraphics[width=1\linewidth]{figs/diffStress_diffVel.pdf}
%	\caption{The change percentage of ice speed (blue dots) and stress components (red dots; a--d represents $\sigma_{p1}$, $\sigma_{p2}$, $\sigma_{f}$ and $\sigma_{s}$, respectively) for all cells at the grounding line corresponding to Fig.~\ref{stressDiff}.}
%	\label{stressDiff_velDiff}
%\end{figure}
